lifespan_eda

### 2024-05-02 eda/lifespan_eda.Rmd
cleaning up, demographics

# #pull plotting functions from github
# plot.func.url <- "https://raw.githubusercontent.com/BGDlab/GAMLSS/main/plotting_functions.R?token=GHSAT0AAAAAACGAYP4HZWCTHACGUM6KG2PSZIQUPBA"
# Sys.setenv(GITHUB_PAT = "") #if needed to access private BGDlab GAMLSS repo
# source_url(plot.func.url) #sometimes doesn't work....?

@@

```{r}
#sample size, sex
length(unique(cn.df.imp$participant))
nrow(cn.df.imp)

@@

>>>>

@@

```{r}
#sample size, sex
length(unique(cn.df.imp$participant))
nrow(cn.df.imp) == length(unique(cn.df.imp$participant))

@@

table(cn.df.imp$sex)["Female"]/nrow(cn.df.imp)
